### 2025-04-05 getting-started.qmd
20250405 - specify package for function

```{r}
players %>%
  select(name, age)

players %>%
  select(name:age)

players %>%
  select(all_of(subsetVars))
```

@@

```{r}
players %>%
  select(-name, -age)

players %>%
  select(-c(name:age))

players %>%
  select(-all_of(dropVars))
```

@@

```{r}
players %>%
  filter(position == "RB") %>%
  select(all_of(subsetVars))
```

@@

```{r}
players %>%
  mutate(across(c(
    oldVar1:oldVar2),
    ~ case_match(
      .,
      c("quarterback","old","running back") ~ 0,
      c("wide receiver","tight end","young") ~ 1)))
```

@@

```{r}
players <- players %>% 
  rename(
    newVar1 = oldVar1,
    newVar2 = oldVar2)
```

@@

players <- players %>% 
  rename_with(~ varNamesTo, all_of(varNamesFrom))
```

@@

```{r}
players %>%
  mutate(across(c(
    ID,
    age),
    as.numeric))

players %>%
  mutate(across(
    age:newVar1,
    as.character))

players %>%
  mutate(across(where(is.factor), as.character))
```

@@

mergeExample1 <- full_join(
  mergeExample1A,
  mergeExample1B,
  by = "player")

@@

mergeExample2 <- full_join(
  mergeExample2A,
  mergeExample2B,
  by = "player")

@@

mergeExample3 <- full_join(
  mergeExample3A,
  mergeExample3B,
  by = "player")

@@

```{r}
fullJoinData <- full_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
leftJoinData <- left_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
rightJoinData <- right_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
innerJoinData <- inner_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
semiJoinData <- semi_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
antiJoinData <- anti_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
crossJoinData <- cross_join(
  players,
  fantasyPoints)

@@

```{r}
dataLong <- full_join(
  players %>% select(-age),
  fantasyPoints_weekly,
  by = c("ID")
)

@@

```{r}
dataWide <- dataLong %>% 
  pivot_wider(
    names_from = c(season, week),
    names_glue = "{.value}_{season}_week{week}",
    values_from = fantasyPoints)

@@

```{r}
dataLong <- dataWide %>% 
  pivot_longer(
    cols = fantasyPoints_2022_week1:fantasyPoints_2023_week17,
    names_to = c("season", "week"),
    names_pattern = "fantasyPoints_(.*)_week(.*)",
    values_to = "fantasyPoints")

>>>>

```{r}
players %>%
  dplyr::select(name, age)

players %>%
  dplyr::select(name:age)

players %>%
  dplyr::select(all_of(subsetVars))
```

@@

```{r}
players %>%
  dplyr::select(-name, -age)

players %>%
  dplyr::select(-c(name:age))

players %>%
  dplyr::select(-all_of(dropVars))
```

@@

```{r}
players %>%
  dplyr::filter(position == "RB") %>%
  dplyr::select(all_of(subsetVars))
```

@@

```{r}
players %>%
  dplyr::mutate(across(c(
    oldVar1:oldVar2),
    ~ case_match(
      .,
      c("quarterback","old","running back") ~ 0,
      c("wide receiver","tight end","young") ~ 1)))
```

@@

```{r}
players <- players %>% 
  dplyr::rename(
    newVar1 = oldVar1,
    newVar2 = oldVar2)
```

@@

players <- players %>% 
  dplyr::rename_with(~ varNamesTo, all_of(varNamesFrom))
```

@@

```{r}
players %>%
  dplyr::mutate(across(c(
    ID,
    age),
    as.numeric))

players %>%
  dplyr::mutate(across(
    age:newVar1,
    as.character))

players %>%
  dplyr::mutate(across(
    where(is.factor),
    as.character))
```

@@

mergeExample1 <- dplyr::full_join(
  mergeExample1A,
  mergeExample1B,
  by = "player")

@@

mergeExample2 <- dplyr::full_join(
  mergeExample2A,
  mergeExample2B,
  by = "player")

@@

mergeExample3 <- dplyr::full_join(
  mergeExample3A,
  mergeExample3B,
  by = "player")

@@

```{r}
fullJoinData <- dplyr::full_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
leftJoinData <- dplyr::left_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
rightJoinData <- dplyr::right_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
innerJoinData <- dplyr::inner_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
semiJoinData <- dplyr::semi_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
antiJoinData <- dplyr::anti_join(
  players,
  fantasyPoints,
  by = "ID")

@@

```{r}
crossJoinData <- dplyr::cross_join(
  players,
  fantasyPoints)

@@

```{r}
dataLong <- dplyr::full_join(
  players %>% dplyr::select(-age),
  fantasyPoints_weekly,
  by = c("ID")
)

@@

```{r}
dataWide <- dataLong %>% 
  tidyr::pivot_wider(
    names_from = c(season, week),
    names_glue = "{.value}_{season}_week{week}",
    values_from = fantasyPoints)

@@

```{r}
dataLong <- dataWide %>% 
  tidyr::pivot_longer(
    cols = fantasyPoints_2022_week1:fantasyPoints_2023_week17,
    names_to = c("season", "week"),
    names_pattern = "fantasyPoints_(.*)_week(.*)",
    values_to = "fantasyPoints")
